Temporary Trade Barriers: \\ When Will They End?

### 2017-11-04 presentation.tex
streamline presentation after jr seminar

\section{Overview}
\subsection{Preview}
\begin{frame}
\frametitle{The Questions}
\pause
\begin{enumerate}[<+->]
	\item How long do deviations from trade agreement tariffs last? 
  \item What are the determinants of renewals?
		\begin{itemize}
			\item They don't happen for \textit{no} reason at all
		\end{itemize}
\end{enumerate}
\end{frame}

\begin{frame}{Institutional Detail}
\begin{itemize}[<+->]
	\item Temporary trade barriers have potential to be renewed
		\begin{itemize}
			\item For Anti-dumping (AD) duties, initial five year term, renewal for five years
			\item For Safeguards, four then four; much rarer than AD
		\end{itemize}
	\item Authorized by WTO
	\item Very little in the agreements to guide the process
		\begin{itemize}
			\item WTO litigation gives gov'ts a LOT of latitude
		\end{itemize}
	\item In U.S., for AD:
		\begin{itemize}
			\item DOC initiates, determines whether dumping would continue
			\item ITC determines whether injury would recur / continue
		\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Economy}
\begin{itemize}
	\item Two countries: home and foreign (${}^*$)
	\item Separable in three goods: $X$ and $Y$ (traded) and numeraire
	\item Demand identical for both goods in both countries
	\item Supply: $Q_X^*(P_X) > Q_X(P_X)$ $\forall P_X$; symmetric for $Y$ 
		\begin{itemize}
			\item Home net importer of $X$, net exporter of $Y$
		\end{itemize}
\end{itemize}

@@

\section{Results}
\subsection{}
\begin{frame}{Timeline}
\begin{enumerate}[<+->]
	\item \textbf{Import-competing firms lobby DOC/ITC to renew AD duties}
	\item \textbf{Uncertainty is resolved}
	\item \textbf{DOC/ITC decide whether to renew duties}
	\item Private actors make production, consumption decisions
\end{enumerate}
\end{frame}

@@

\vskip.2in
\pause
Magnitudes are not directly comparable
\begin{itemize}
	\item Working to endogenize $\tau^{\textit{ad}}$
\end{itemize}

@@

\section{Conclusion}
\subsection{}
\begin{frame}{Future Work}
\pause
\begin{itemize}[<+->]
	\item Comparative static on uncertainty measure
	\item Empirical work
	\item Extend model to include initial decision to grant protection.
		\begin{itemize}
			\item Explain variation in a lobby's incentives between original application of AD and renewal
			\item Lobby's choice between investing in productive vs. rent-seeking behavior while protected
		\end{itemize}
\end{itemize}
\end{frame}

>>>>

\section{Overview}
\subsection{Preview}
\begin{frame}
\frametitle{The Questions}
\pause
\begin{enumerate}[<+->]
	\item How long do deviations from trade agreement tariffs last? 
  \item What are the determinants of renewals?
\end{enumerate}
\end{frame}

\begin{frame}{Institutional Detail}
\begin{itemize}[<+->]
	\item Temporary trade barriers have potential to be renewed
		\begin{itemize}
			\item For Anti-dumping (AD) duties, initial five year term, renewal for five years
			\item For Safeguards, four then four; much rarer than AD
		\end{itemize}
	\item Authorized by WTO
	\item Agreements / litigation provide a LOT of latitude
	\item In U.S., for AD:
		\begin{itemize}
			\item DOC initiates, determines whether dumping would continue
			\item ITC determines whether injury would recur / continue
		\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Economy}
Two countries: home and foreign (${}^*$)
\begin{itemize}
	\item Symmetric and separable in $X$ and $Y$ (traded) and numeraire
		\begin{itemize}
			\item Home net importer of $X$, net exporter of $Y$
		\end{itemize}		
\end{itemize}

@@

\section{Results}
\subsection{}

\begin{comment}
\begin{frame}{Timeline}
\begin{enumerate}[<+->]
	\item \textbf{Import-competing firms lobby DOC/ITC to renew AD duties}
	\item \textbf{Uncertainty is resolved}
	\item \textbf{DOC/ITC decide whether to renew duties}
	\item Private actors make production, consumption decisions
\end{enumerate}
\end{frame}
\end{comment}

@@

\vskip.2in
\pause
Magnitudes are not directly comparable
\begin{itemize}
	\item Work in progress: endogenize $\tau^{\textit{ad}}$
\end{itemize}

@@

\section{Conclusion}
\subsection{}
\begin{frame}{Future Work}
\pause
\begin{itemize}[<+->]
	\item Empirical work
	\item Comparative static on uncertainty measure
	\item Extend model to include initial decision to grant protection.
		\begin{itemize}
			\item Explain variation in a lobby's incentives between original application of AD and renewal
			\item Lobby's choice between investing in productive vs. rent-seeking behavior while protected
		\end{itemize}
\end{itemize}
\end{frame}
